---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# frbca

<!-- badges: start -->
<!-- badges: end -->

The goal of frbca is to conduct benefit-cost analysis (BCA) for buildings
archetypes designed for functional recovery. The inputs include:

- Expected Annualized Losses (EALs) for (i) a baseline (code-conforming) design
  and (ii) recovery-based design interventions
- Structural and nonstructural costs for both (i) and (ii)
- A list of analysis parameters, including discount rate, time horizon, and
  economic analysis parameters such as business income

## Installation

You can install the development version of frbca like so:

You can install frbca from [GitHub](https://github.com) with:

```{r}
devtools::install_github("juanfung/frbca")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(frbca)
## basic example code
```

